\section{Experience}
\titleAndDate{Imperial College London (Large Scale Data and Systems Group)}{October 2024 - Present}
  \italicText{Doctoral Researcher}
  \begin{itemize}[leftmargin=10pt]
    \vspace{-1pt}
    \item\normalText{Investigating efficient scheduling and resource allocation for dynamic LLM-applications such as RAG, inference-time scaling search algorithms, multi-turn chat and ReAct agents.}
    \item\normalText{Exploring efficient co-location of multiple local models, and exploiting heterogenous predictability of dynamic LLM-applications.}
    \item\normalText{Accelerating my research process with large-scale, hierarchical embedding databases of papers from ArXiv/systems and AI conferences.}
  \end{itemize}

  \vspace{4pt}

  \titleAndDate{Imperial College London}{May 2024 - Present}
  \italicText{Cloud Infrastructure}
  \begin{itemize}[leftmargin=10pt]
    \vspace{-1pt}
    \item\normalText{Creating a heterogenous bare-metal cloud of 100 machines serving 30 researchers, optimised for high-performance experimentation.}
    \item\normalText{Enabling fast networking, remote OS provisioning, scalable machine configuration, hardware monitoring, network-attached storage. }
  \end{itemize}

  \vspace{4pt}

  \titleAndDate{BidFX}{April 2023 - August 2023}
  \italicText{Core Engineer}
  \begin{itemize}[leftmargin=10pt]
    \vspace{-1pt}
    \item\normalText{Primarily responsible for design and implementation of the most complex component of a high-performance FIX pricing service, providing pricing to all downstream Foreign Exchange trading services.}
    \item\normalText{Consulted/paired with industry leaders to implement Continuous Delivery on our team; utilized thorough testing + TDD, pair programming, small+frequent PRs, incremental architecture and refactoring, optimizing test suites, builds, and pipelines for fast feedback, tickets+docs on the fly.}
    \item\normalText{Optimized a complex Java application for \begin{math}\mu\end{math}s tail-latency, utilizing profiling, object pooling for garbage elimination, single-threading, NIO, many compression mechanisms. Exercising understanding and manipulating the JVM/OS/network/hardware interactions.}
  \end{itemize}
  
  \vspace{4pt}
  
  \titleAndDate{Cub3 Inc}{June 2022 - August 2022}
  \italicText{Backend Engineer, Managed 1-2 Junior Devs}
  \begin{itemize}[leftmargin=10pt]
    \vspace{-1pt}
    \item\normalText{Architected and wrote a gRPC backend in Typescript (including Solana blockchain services, Primsa DB, extensible permissioning system) enabling custodial wallet management and NFT collection creation.}
  \end{itemize}

  \vspace{-15pt}
  